\Title

### 2015-09-04 moho-inversion.tex
Reorganize inv formulation a bit

\noindent in which $d_i$ is the $i$th element of the predicted data vector
$\mbf{d}$, $\mbf{p}$ is the parameter vector containing the Moho depths
($z_k$),
and
$f_i$ is the $i$th non-linear function that maps the parameters onto the data.

@@

\noindent $\Gamma(\mbf{p})$ is non-linear with respect to $\mbf{p}$.
Thus, we can find the minimum of the goal function using gradient-based
iterative optimization
methods like the Gauss-Newton method or the Steepest Descent method.
Such methods start from an initial estimate $\mbf{p}^0$ and  repeatedly update
the estimate.
The update at the $k$th iteration $\mbf{\Delta p} = \mbf{p}^{k+1} - \mbf{p}^k$
for the Gauss-Newton method is

@@

\noindent in which
$\mbf{H}$ is the Hessian matrix of $\Gamma$,

\begin{equation}
    \mbf{H}(\mbf{p}^k) = 2\mbf{A}(\mbf{p}^k)^T\mbf{A}(\mbf{p}^k) +
    2\mu\mbf{R}^T\mbf{R},
\end{equation}

\noindent
$\mbf{\nabla}\Gamma$ is the gradient vector of $\Gamma$,

\begin{equation}
    \mbf{\nabla}\Gamma(\mbf{p}^k) = -2\mbf{A}(\mbf{p}^k)^T[\mbf{d}^o - \mbf{d}] +
    2\mu\mbf{R}^T\mbf{R}\mbf{p}^k,
\end{equation}

\noindent and
$\mbf{A}$ is the Jacobian or sensitivity matrix,

\begin{equation}
    A_{ij} = \dfrac{\partial f_i}{\partial p_j}(\mbf{p}).
\end{equation}

Steepest has poor convergence when close to the solution
\citep{kelley_iterative_1987}.

>>>>

\noindent in which $d_i$ is the $i$th element of the $N$-dimensional predicted
data vector $\mbf{d}$, $\mbf{p}$ is the $M$-dimensional parameter vector
containing the Moho depths ($z_k$),
and $f_i$ is the $i$th non-linear function that maps the parameters onto the
data.

@@

\noindent $\Gamma(\mbf{p})$ is non-linear with respect to $\mbf{p}$.
Thus, we can find the minimum of the goal function using gradient-based
iterative optimization
methods like the Gauss-Newton or Steepest Descent methods.
Such methods start from an initial estimate $\mbf{p}^0$ and repeatedly update
the estimate until a minimum of the goal function is reached.

The update at the $k$th iteration $\mbf{\Delta p} = \mbf{p}^{k+1} - \mbf{p}^k$
for Gauss-Newton method is

@@

\noindent in which
$\mbf{\nabla}\Gamma$ is the gradient vector and
$\mbf{H}$ is the Hessian matrix of $\Gamma$.
The gradient is given by

\begin{equation}
    \mbf{\nabla}\Gamma(\mbf{p}^k) =
    -2\mbf{A}^T[\mbf{d}^o - \mbf{d}] +
    2\mu\mbf{R}^T\mbf{R}\mbf{p}^k,
    \label{eq:gradient}
\end{equation}

\noindent in which
$\mbf{A}$ is the Jacobian or sensitivity matrix,

\begin{equation}
    A_{ij} = \dfrac{\partial f_i}{\partial p_j}(\mbf{p^k}).
\end{equation}

\noindent
In practice, the derivative above is often calculated through a first-order
finite-difference approximation.

The first term of \eq{gradient} is the gradient of the data-misfit
function $\phi$ and the second term is the gradient of the regularizing
function $\theta$.

The Hessian matrix is given by

\begin{equation}
    \mbf{H}(\mbf{p}^k) = 2\mbf{A}^T\mbf{A} +
    2\mu\mbf{R}^T\mbf{R}.
    \label{eq:hessian}
\end{equation}

\noindent
The first term of \eq{hessian} is the Gauss-Newton approximation of the Hessian
matrix of $\phi$ and the second term is the Hessian of $\theta$.

The Steepest Descent method uses only the gradient direction to
update the initial estimate,

\begin{equation}
    \mbf{\Delta p} = -\mbf{\nabla}\Gamma(\mbf{p}^k).
\end{equation}

\noindent
Because of this, the Steepest Descent method has poor convergence when the
current solution is close to the minimum of the goal function
\citep{kelley_iterative_1987}.

Both methods require the computationally expensive evaluation of the Jacobian
matrix $\mbf{A}$.
\todo{Talk a bit about why this is slow and difficult}
